### 2023-11-14 main.tex
:)

In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula is follows from the ground state $|\Psi^{'}\rangle$found in \eqref{ABS_1}.

@@

			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
			\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})

@@

\end{proposition} %Therefore, 

@@

%where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 

@@

			where the expectation can be computed using \eqref{exactCorrelations}. 

@@

			\begin{proposition}[Normalization of $|\Psi\rangle$]
				The steady state is normalized, i.e.
					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1

@@

			\textbf{Proof}: here we write  
					\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,w_{b}\}\\
			We aim to show that 
				&\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

@@

				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1

@@

				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0

@@

				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\

@@

>>>>

In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula follows from the ground state $|\Psi^{'}\rangle$ found in \eqref{ABS_1}.

@@

	and where 
			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)
	%		\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
	%		\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})

@@

\begin{remark}[Equilibrium case]
	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ only the terms with $c_{x}=0$ do survive in \eqref{SteadyState-coeff-implicit}. Therefore we obtain 
		\Psi(\bm{\tau})=\prod_{a=1}^{N}\beta_{a}^{\sum_{x=1}^{L}\delta_{\tau_{x},a}}
i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $p_{a}=\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 
\begin{remark}[Implicit form of $\Psi(\bm{\tau})$]
	The elements of the the vector $|\Psi\rangle$ can also be written as a linear combination of elements $\Psi^{'}(\bm{\tau})$ as 
	\begin{equation}\label{implicit-steadyState}
		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
	\begin{equation}\label{notation-PSI}
			\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\

%Therefore, 

@@

where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 

@@

			where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 

@@

			\begin{proposition}[Normalization]
				The steady state $|\Psi\rangle$ is normalized, i.e.
					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=1

@@

			\textbf{Proof}: Considering \eqref{notation-PSI}, we aim to show that 
				\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

@@

				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1

@@

				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0

@@

				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\

@@

\paragraph{$|\Psi\rangle$ for SSEP}
In the colour-blind case we have that 
	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})|\bm{\tau}\rangle
	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},2}\right)\sum_{s=0}^{|\bm{\tau}|+b}(\alpha-\beta)^{s}\beta^{L-s}\sum_{1\leq \ell_{1}<\ldots<\ell_{s}\leq |\bm{\tau}|}\prod_{k=1}^{s}\frac{\left(L+1-x_{\ell_{k}}-s+k\right)}{(2+L-k)}
	|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1} \dt
\textbf{Proof}: the proof follows from \eqref{implicit-steadyState} and \eqref{PsiI-N2}. 
